Staged Abstract Interpreters

### 2019-04-06 paper/60_cases.tex
paper

In this section, to demonstrate the SAI approach is widely applicable, we extend
and refactor the staged abstract interpreter we presented in Section \ref{sai}
to various control-flow analysis (CFA). We first discuss calling-context
sensitive analysis for staged analyzers by tweaking allocation strategy; then we
will see how to implement store-widening with staged monads, which is a common
optimization in CFA; finally, we integrate abstract garbage collection with
staging.

@@

@@

\paragraph{Partially-Static Context} Under a polyvariant analysis (like
$k$-CFA), such summary generated by specializing static analyzer even could do
more for calling context by partially-static data optimization. For example,
consider that we have a library consists of three functions @f@, @g@ and @h@,
where @f@ calls @g@ and @h@ internally and returns @y@ fianlly (we extend the
language to have multiple arguments). @g@ and @h@ do not depend on @f@. Now we
would like to modularlly specialize these functions, starting from @f@.

>>>>

In this section, to demonstrate the SAI approach is widely applicable, we extend
and refactor the staged abstract interpreter we presented in Section \ref{sai}
to various control-flow analysis (CFA). We first discuss calling-context
sensitive analysis for staged analyzers by tweaking allocation strategy; then we
will see how to implement store-widening with staged monads, which is a common
optimization in CFA; finally, we integrate abstract garbage collection with
staging. All of them are in fact orthogonal to staging.

@@

Abstract garbage collection is a technique to reclaim unreachable addresses in
the store while doing the abstract interpretation
\cite{Might:2006:IFA:1159803.1159807}. \citet{DBLP:journals/pacmpl/DaraisLNH17}
shows that, for big-step monadic abstract interpreter, we may add a @Reader@
monad to track a set of root addresses and compute the reachable addresses every
time when we obtain a value.

\begin{lstlisting}
  def ask_root: AnsM[Set[Addr]]
  def eval(e: Expr): AnsM
\end{lstlisting}

@@

\paragraph{Partially-Static Context} Under a polyvariant analysis (like
$k$-CFA), such summary generated by specializing static analyzer even could do
more for calling context by partially-static data optimization. For example,
consider that we have a library consists of three functions @f@, @g@ and @h@,
where @f@ calls @g@ and @h@ internally and returns @y@ fianlly (we extend the
language to have multiple arguments). @g@ and @h@ do not depend on @f@. Now we
would like to modularlly specialize these functions, starting from @f@ with an
initial environment containing @f@, @g@ and @h@.
